POMDP comparisons across sigma_m, sigma_g

### 2017-12-28 appendix/appendix.Rmd
tidy code blocks up a bit

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
devtools::install("..")
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, dev="CairoPDF", fig.width=7, fig.height=7)
library(tidyverse)
library(gridExtra)
library(ggthemes)
colours <- ptol_pal()(2)
```

```{r suggested_libs}
library(hrbrthemes)
library(extrafont)
##extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
hrbrthemes::import_roboto_condensed()     # One-time use to set up fonts 
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
#ggplot2::theme_set(theme_bw()) # simpler theme if you do not have these fonts
```

```{r helper_routines, include = FALSE}
## map cts values to nearest grid indices 
index <- function(x, grid) map_int(x, ~ which.min(abs(.x - grid)))

det_simulations <- function(x0 = 1/6, Tmax = 20, 
                              B_MSY = K / 2, 
                              F_MSY = r / 2 , 
                              F_PGY = 0.8 * F_MSY){

  msy_policy <- function(x) F_MSY * x
  pgy_policy <- function(x) F_PGY * x
  det_policy <- function(x) pmax(f(x,0) - B_MSY,0) ## ASSUMES harvest takes place *after* recruitment
  reed_policy  <- function(x) pmax(x - B_MSY,0) ## Optimal when harvest takes place *before* recruitment, assumes we are seeing a pre-harvest size.
  ## consequently, if we use such a policy when we are seeing a the post-harvest size, we give too much buffer.

  # a simulation function
  det_sim <- function(policy, f, x0, Tmax){
    action <- state <- obs <- as.numeric(rep(NA,Tmax))
    state[1] <- x0
    for(t in 1:(Tmax-1)){
      obs[t] <- state[t]

      action[t] <- policy(obs[t])
      state[t+1] <- f(state[t], action[t]) 
    }
    data.frame(time = 1:Tmax, state, action, obs)
  }

  # simulate each policy, returning all results in a single unified data frame 
  sims <- 
    list(msy = msy_policy, 
         det = det_policy, 
         pgy = pgy_policy
         #opt = reed_policy
         ) %>% 
    map_df(det_sim, 
           f, x0, Tmax, 
           .id = "method")

  sims
}
```

```{r message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
```

```{r}
options(mc.cores=parallel::detectCores())
```

@@

@@

```{r}

>>>>

```{r message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)

ggplot2::theme_set(theme_bw())
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)

options(mc.cores=parallel::detectCores())
```

```{r suggested_libs, include=FALSE, eval=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, dev="CairoPDF", fig.width=7, fig.height=7)
devtools::install("..", dep=TRUE)
library(gridExtra)
library(ggthemes)
colours <- ptol_pal()(2)
library(hrbrthemes)
library(extrafont)
##extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
hrbrthemes::import_roboto_condensed()     # One-time use to set up fonts 
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

@@

```{r helper_routines}
## map cts values to nearest grid indices

det_simulations <- function(x0 = 1/6, Tmax = 20, 
                              B_MSY = K / 2, 
                              F_MSY = r / 2 , 
                              F_PGY = 0.8 * F_MSY){
  msy_policy <- function(x) F_MSY * x
  pgy_policy <- function(x) F_PGY * x
  det_policy <- function(x) pmax(f(x,0) - B_MSY,0) ## ASSUMES harvest takes place *after* recruitment

  det_sim <- function(policy, f, x0, Tmax){
    action <- state <- obs <- as.numeric(rep(NA,Tmax))
    state[1] <- x0
    for(t in 1:(Tmax-1)){
      obs[t] <- state[t]
      action[t] <- policy(obs[t])
      state[t+1] <- f(state[t], action[t]) 
    }
    data.frame(time = 1:Tmax, state, action, obs)
  }

  # simulate each policy, returning all results in a single unified data frame 
  list(msy = msy_policy, det = det_policy, pgy = pgy_policy) %>% 
    map_df(det_sim, f, x0, Tmax, .id = "method") 
}
```

@@

```{r}
# map to grid
index <- function(x, grid) map_int(x, ~ which.min(abs(.x - grid)))
